### 2014-03-07 src/analysis.Rnw
udpate

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

First, we ran the the mutation analysis to identify the general distribution of mutants within our set of projects.
This provided us with the relative number of each mutation operators, that are produced, and also the general number of
mutants generated by each operator that was detected. This is given in Figure~\ref{fig:op}.

>>>>

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

First, we ran the the mutation analysis to identify the general distribution of mutants within our set of projects.
This provided us with the relative number of each mutation operators, that are produced, and also the general number of
mutants generated by each operator that was detected. This is given in Figure~\ref{fig:op}. This suggests that the operators
are distributed in the following order: \pitnvmc, \pitnc, \pitrc, \pitdc, \pitrv, \pitic, \pitcc, \pitemv, \pitvmc, \pitm,
\pitcb, \piti, \pitri, \pitrs, \pites, \pitin. We use this information later for n-selective mutation.

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Analysis of Sampling Criteria}
% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
<<>>=
odata <- subset(stats.df, s.element=='project' & strategy=='xpercentperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='project' & strategy=='xpercentperunit' & kind=='randoop')
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='green')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]
